The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-02-10 VonHolzenBergmann_MPMetaAnalysis.Rmd
Huge page cuts to meet DevPsych requirements

documentclass     : "apa6"
classoption       : "man"
output            :
  papaja::apa6_pdf:
    latex_engine: xelatex

@@

header-includes:
  - \usepackage{setspace}
  - \usepackage{fontspec}
  - \usepackage{tipa}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
---

@@

@@

### Load libraries
library(papaja)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)
library(xtable)
library(schoRsch)
library(multcomp)
library(poibin)
library(tidyverse)

@@

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). Twenty years' worth of studies have examined infants' application of phonological category knowledge during word recognition through the mispronunciation sensitivity paradigm to probe the development of this latter distinction. At this point, a picture on the functional use of language-specific phonetic and phonological knowledge began to emerge. At the turn of the millennium, infant language acquisition researchers had begun to explore the phonetic information that infants attend to while segmenting words from the speech stream [@Jusczyk1995] and learning minimal pairs [@Stager1997]. Both studies and the lines of research they sparked showed that under the right conditions, even young infants can use their emerging native language phonological skills during word-level language processing.
@Swingley2000 expanded this exploration to infants's existing representations, investigating how infants interpret phonological variation in familiar word recognition. American-English learning 18- to 23-month-olds were presented with pairs of images of words they were very likely to know (e.g. a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g. "baby") or a mispronounced label (e.g. "vaby") for one of the images. Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels. @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified.

Why should sensitivity to mispronunciations pose a challenge to the young infant and thus the findings of @Swingley2000 be found novel? There are two key challenges the infant learner has to contend with. First, the native language being learned determines the relevant contrasts for the infant language-learner. These contrasts are therefore not innate, but must be learned. For an infant learning Catalan, the vowel contrast /e/-/\textipa{E}/ signifies a change in meaning, whereas this is not the case for an infant learning Spanish. Second, across talkers, these sounds might be realized differently, and change even as the talker talks to an infant or adult [e.g. @Benders2013]. As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired and applied to lexical representations. The time is thus ripe to aggregate all publicly available evidence using a meta-analysis. In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @Frank2017; @MB1; for notable exceptions). Before we outline the meta-analytical approach and its advantages in detail, we first discuss the proposals this study seeks to disentangle and the data supporting each of the accounts.

Regarding the change in mispronunciation sensitivity over development, only roughly half of studies have compared more than one age group on the same mispronunciation task (see Table \@ref(tab:SummaryTable)) and of those, all possible patterns of development are found. This renders conclusions regarding developmental change in mispronunciation sensitivity difficult. Given the diverse evidence for developmental change, or lack thereof, the question arises as to what could be driving these differences. We thus summarize the existing empirical evidence, as well as developmental and methodological explanations for an increase, a decrease, or unchanged sensitivity to mispronunciations throughout infancy.

An *increase* in mispronunciation sensitivity is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. More precisely, the difference in target looking for correct and mispronounced trials is reported to be smaller in younger infants and grows as infants develop. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. According to PRIMIR [@Curtin2011; @Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task. A growing vocabulary also reflects increased experience or familiarity with words, which may sharpen the phonological detail of their representations [@Barton1980]. This argument is supported by the results of @Mani2010kepstups. Here, 12-month-old infants were divided into low and high vocabulary groups. High vocabulary infants showed greater sensitivity to vowel mispronunciations than low vocabulary infants, although this was not the case for consonant mispronunciations (see below for further discussion on consonant-vowel assymmetry). If increasing age and/or vocabulary growth leads to an increase in the phonological specificity of infants' word representation, we should find a relationship of either with mispronunciation sensitivity.

@@

There are no theoretical accounts that would predict *decreased* mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations . @Mani2011 tested 18- and 24-month-olds' sensitivity to increasingly larger mispronunciations: 1- (bed-bud), 2- (foot-fit), and 3-feature phonological changes (doll-deal). Although both age groups were sensitive to mispronunciations overall, 18- but not 24-month-olds showed sensitivity to more subtle 1-feature mispronunciations. To account for this pattern of results, the authors suggest that when faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below), as @Mani2011 found with 24-month-olds in their study. In contrast, 18-month-olds did not show graded sensitivity, showing similar disruptions to word recognition for smaller and larger mispronunciations.

To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size. But, this may not account for all variability found in the literature. Although infant mispronunciation sensitivity studies are generally interested in the phonological detail with which infants represent familiar words, many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that overlaps with the target image in the onset phoneme or a completely novel, unfamiliar distractor image. These experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. We thus follow our analyses of a developmental trajectory with one of features of the task, and line out here task effects which can shed further light on early phono-lexical representations and their maturation.

The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2011; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment. In a particularly demanding task, such as when the target and distractor image share the same onset (e.g. doggie and doll), infants' ability to access the phonological detail of familiar words may be restricted [@Swingley1999]. If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies. Note, however, that those studies reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages .

The manipulations that might increase task demands, such as overlap between target and distractor, are also theoretically interesting, focusing on issues at the intersection of phonological development and lexical processing. For specific questions where we can aggregate multiple studies, we take the opportunity to shine a meta-analytic light on what modulates infants' ability to detect mispronunciations in follow-up analyses. We outline first which nuanced questions have been frequently asked to provide a more in-depth overview of the current literature.

@@

The *position of mispronunciation* in the word may differentially interrupt the infant's word recognition process, with onset mispronunciations leading to greater mispronunciation sensitivity than medial or coda mispronunciations. Models of spoken word processing place more or less importance on the position of a phoneme in a word. The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations.

Consonantal changes may be more disruptive to lexical processing than vowel changes in both adults [@Nazzi2018] and infants [@Nazzi2016], known as the consonant bias. A learned account predicts that a consonant bias emerges over development [@Floccia2014; @Nazzi2016; @Keidel2007] and that this emergence is impacted by the language family of the infants' native language [@Nazzi2016]. In mispronunciation sensitivity, this would first translate to consonant mispronunciations impairing word recognition to a greater degree than vowel mispronunciations. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups] and Danish-learning infants [@Hojen] and do not compare infants learning different native languages [for cross-linguistic evidence from word-learning see @Nazzi2009a]. One study with English-learning infants did find weak evidence for greater sensitivity to consonant compared to vowel mispronunciations [@Swingley2016]. In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to assess the predictions of the learned account of the consonant bias.

A second set of questions is whether the context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a vowel mispronunciation of the target word "doggie", the image of a dog would be paired with a distractor image that shares onset overlap, such as "doll". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Swingley1999]. Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change. Note that in this case, the mispronunciation is necessarily either word-medial or –final, thus possibly creating an interaction between mispronunciation position and phonological overlap.

We may find that if mispronunciation sensitivity changes as children develop, that this change is modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar. This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared. Most studies present infants with pictures of two known objects, thereby ruling out the unlabeled competitor, or distractor, as possible target. It is thus not surprising that infants tend to look towards the target more, even when its label is mispronounced. In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016]. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003], an ability that is developing from 18 to 30 months [@Bion2013].

@@

apa_table(Sum_table, col.names = c("Paper", "Format", "Age", "Vocabulary", "Familiarity", "Target Overlap", "Size", "Position", "Type", "N Effect Sizes"), caption = "Summary of all studies. Age: mean age(s) reported in the paper (in months). Vocabulary: Comp = comprehension, Prod = production. Distractor Familiarity: Fam = Familiar Distractor, Unfam = Unfamiliar Distractor. Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda. Mispronunciation Size: number of features changed; commas indicate when sizes were compared separately (e.g. 1, 2, 3), dashes indicate the range of sizes were aggregated (e.g. 1-3). Mispronunciation Position: O = onset, M = medial, C = coda. Mispronunciation Type: C = consonant, V = vowel, T = tone. For both Mispronunciation Position and Type, a slash separator indicates that is was tested but a distinction was not made in the stimuli. For all categories, unspec. indicates that the value was unspecified in the paper", landscape = TRUE, font_size = "scriptsize", col_spanners = list(`Distractor` = c(5, 6), `Mispronunciation` = c(7, 9)))

@@

The `r length(unique(descriptive_dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible [@Tsuji2014; @Bergmann2018]. For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results. For the planned analyses to evaluate the development of mispronunciation sensitivity and modulating factors, we focus on the following characteristics:

1. Condition: Were words mispronounced or not;
2. Mean age reported per group of infants, in days; 
3. Vocabulary size, measured by a standardized questionnaire or list;
4. Size of mispronunciation, measured in features changed;
5. Position of mispronunciation: onset, medial, offset, or mixed;
6. Type of mispronunciation: consonant, vowel, or both;
7. Phonological overlap between target and distractor: onset, onset/medial, rhyme, none, novel word;
8. Distractor familiarity: familiar or unfamiliar

A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results [^1]. We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  [e.g., consonant versus vowel mispronunciations; @Mani2007].  The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were `r nrow(descriptive_dat)` records in our data.

@@

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers). Two papers reported raw means and standard deviations for some records and just t-values for the remaining records [@Swingley2016; @Altvater2014]. Raw means and standard deviations were extracted from figures for `r with(descriptive_dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participant design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance. Upon request we were provided with correlation values for one paper [@Altvater2010]; we were able to compute correlations using means, standard deviations, and t-values for `r with(corr_info, n_unique[imputed_corr == "no"])` papers [following @Csibra2016; see also @Rabagliati2018]. Correlations were imputed for the remaining papers [see @Black2017 for the same procedure]. For two papers, we could not derive any effect size [@Ballem2005; @Renner2017], and for a third paper, we do not have sufficient information in one record to compute effect sizes [@Skoruppa2013]. We compute a total of `r sum(dat$is_mp == 0)+n_outlier_correct` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)+n_outlier_MP` for mispronunciations. Following standard meta-analytic practice, we remove outliers, i.e. effect sizes more than 3 standard deviations from the respective mean effect size. This leads to the exclusion of `r n_outlier_correct` records for correct pronunciations and `r n_outlier_MP` records for mispronunciations.

@@

Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper. Most papers (*n* = `r with(comparison_info, count[within_measure == "pre_post_naming_effect"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post_naming_effect"])` papers) subtracted the PTL score for a pre-naming baseline phase from the PTL score for a post-naming phase and report a difference score. Other papers either compared post- and pre-naming PTL with one another (*n* = `r with(comparison_info, count[within_measure == "pre_post"])` records from `r with(comparison_info, n_unique[within_measure == "pre_post"])` papers), thus reporting two variables, or compared post-naming PTL with a chance level of 50% (*n* = `r with(comparison_info, count[within_measure == "post"])` records from `r with(comparison_info, n_unique[within_measure == "post"])` papers). For all these comparisons, positive values or values above 50% (either as reported or after subtraction of chance level or a pre-naming baseline PTL) indicate target looks towards the target object after hearing the label, i.e. a recognition effect. Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

@@

```{r FunnelCombo, echo = FALSE, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size. The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot asymmetry.", results="hide"}

@@

We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels. The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`. This is a small to medium effect size [according to the criteria set by @Mills-Smith2015]. That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants tended to fixate on the corresponding object. Although the publication bias present in our analysis of funnel plot asymmetry suggests that the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)`, which is substantially above zero, together suggest that this result is somewhat robust. In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.

@@

sum_eff <- coef(summary(rma_MP))[1,]

@@

We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size was `r g_SE(sum_eff)` which was also significantly different from zero `r CI_p(sum_eff)`. This is considered a small effect size [@Mills-Smith2015], but significantly above zero, which suggests that even when presented with a mispronounced label, infants fixated the correct object. In other words, infants are able to resolve mispronunciations, a key skill in language processing We again note the publication bias (which was smaller in this condition), and the possibility that the effect size may be overestimated. But, as the p-curve indicated evidential value, we are confident in the overall pattern, namely that infants fixate the target even after hearing a mispronounced label.

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly. To this end, we combined the two datasets. When condition was included (correct, mispronounced), the moderator test was significant (`r mod_test(rma_MPeffect)`). The estimate for mispronunciation sensitivity was `r g_SE(sum_eff)`, and infants' looking behavior across conditions was significantly different `r CI_p(sum_eff)`. This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations. In other words, we observe a significant difference between the two conditions and can now quantify the modulation of fixation behavior in terms of standardized effect sizes and their variance. This first result has both theoretical and practical implications, as we can now reason about the amount of perturbation caused by mispronunciations and can plan future studies to further investigate this effect with suitable power.

@@

The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the most frequently observed sample size is `r median_sample` participants. If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is `r ptt_power`%. In other words, only about half the studies should report a significant result even with a true population effect. Reversely, to achieve 80% power, one would need to test `r round(ptt.est$n, 0)` participants. While this number does not seem to differ dramatically from the observed sample sizes, the impact of the smaller sample sizes on power is thus substantial and should be kept in mind when planning future studies. Furthermore, many studies in this meta-analysis included further factors to be tested, leading to two-way interactions (age versus mispronunciation sensitivity is a common example), which by some estimates require four times the sample size to detect an effect of similar magnitude as the main effect for both ANOVA [@Fleiss1986] and mixed-effect-model [@Leon2009] analyses. We thus strongly advocate for a consideration of power and the reported effect sizes to test infants’ mispronunciation sensitivity and factors influencing this ability.

@@

### Vocabulary Size: Correlation Between Mispronunciation Sensitivity and Vocabulary

@@

#### Offset time after target naming

>>>>

documentclass     : "apa6"
classoption       : "man, noextraspace"
output            :
  papaja::apa6_pdf:
    latex_engine: xelatex

@@

header-includes:
  - \usepackage{setspace}
  - \usepackage{fontspec}
  - \usepackage{tipa}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
  - \AtBeginEnvironment{tablenotes}{\doublespacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1.5}}
  - \captionsetup[table]{font=scriptsize}
---

@@

# removing authornote for now to save space

# authornote: |
#   The authors would like to thank Emelyne Gaudichau for valuable assistance in entering data. Author 1 was supported by the Agence Nationale de la Recherche (ANR-13-BSH2-0004) and by training grant DC-00046 from the National Institute of Deafness and Communicative Disorders of the National Institutes of Health. Author 2 was supported by the European Horizon 2020 programme (Marie Skłodowska-Curie grant No 660911), the Agence Nationale de la Recherche (ANR-10-IDEX-0001-02 PSL*, ANR-10-LABX-0087 IEC) and the Fondation de France. The authors each declare that they have no conflict of interest.

@@

### Load libraries
library(papaja)
library(metafor)
library(meta)
library(pwr)
library(knitr)
library(ggplot2)
library(wesanderson)
library(grid)
library(gridExtra)
library(xtable)
library(schoRsch)
library(multcomp)
library(poibin)
library(tidyverse)
library(kableExtra)

@@

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). This meta-analysis examines on the latter, focusing how infants apply the relevant phonological categories of their native language, aggregating twenty years' worth of studies using the mispronunciation sensitivity paradigm. The original study of @Swingley2000 presented American-English learning 18- to 23-month-olds with pairs of images of words they were very likely to know (e.g. a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g. "baby") or a mispronounced label (e.g. "vaby") for one of the images. Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels. @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified. As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired and applied to lexical representations. The time is thus ripe to aggregate all publicly available evidence using a meta-analysis. In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @MB1 for a notable exception).

An *increase* in mispronunciation sensitivity with age is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. According to PRIMIR [@Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task. This argument is supported by the results of @Mani2010kepstups, who found that 12-month-old infants with a larger vocabulary showed a greater sensitivity to vowel mispronunciations than infants with a smaller vocabulary.

@@

There are no theoretical accounts that would predict *decreased* mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations. Here, 18- but not 24-month-old infants showed sensitivity to more subtle mispronunciations that differed from the correct pronunciation by 1 phonological feature [@Mani2011]. When faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below), as @Mani2011 found with 24- but not 18-month-olds in their study.

To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size. But, this may not account for all variability found in the literature. Many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that is either familiar or completely novel. We thus include an analysis of the features of the task to shed further light on early phono-lexical representations and their maturation.

These research questions and experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment. In a particularly demanding task, such as when the target and distractor image share the same onset (e.g. doggie and doll), infants' ability to access the phonological detail of familiar words may be restricted [@Swingley1999]. If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies. Note, however, that those studies reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages.

@@

The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations. To evaluate these competing theories, studies often manipulate the *mispronunciation position*, whether onset, medial, or coda, in the word.

Consonantal changes may be more disruptive to lexical processing than vowel changes, known as the consonant bias, and a learned account predicts that this bias emerges over development and is impacted by the language family of the infants' native language [for a review see @Nazzi2016]. Yet, the handful of studies directly comparing sensitivity to consonant and vowel mispronunciations mostly find symmetry as opposed to an asymmetry between consonants and vowels for English- [@Mani2007; @Mani2010kepstups; but see @Swingley2016] and Danish-learning infants [@Hojen] and do not compare infants learning different native languages [for cross-linguistic evidence from word-learning see @Nazzi2009a]. In the current meta-analysis, we examine infants' sensitivity to the *type of mispronunciation*, whether consonant or vowel, across different ages and native language families to assess the predictions of the learned account of the consonant bias.

A second set of questions is whether the context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a vowel mispronunciation of the target word "doggie", the image of a dog would be paired with a distractor image that shares onset overlap, such as "doll". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Swingley1999]. Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.

Mispronunciation sensitivity may also be modulated by *distractor familiarity*: whether the distractor used is familiar or unfamiliar. This is a particularly fruitful question to investigate within the context of a meta-analysis, as mispronunciation sensitivity in the presence of a familiar compared to unfamiliar distractor has not been directly compared. Most studies present infants with pictures of two known objects, thereby ruling out the unlabeled competitor, or distractor, as possible target. It is thus not surprising that infants tend to look towards the target more, even when its label is mispronounced. In contrast, other studies present infants with pairs of familiar (labeled target) and unfamiliar (unlabeled distractor) objects [@White2008; @Mani2011; @Skoruppa2013; @Swingley2016]. By using an unfamiliar object as a distractor, the infant is presented with a viable option onto which the mispronounced label can be applied [@Halberda2003; @Markman2003].

@@

apa_table(Sum_table, col.names = c("Paper", "Format", "Age", "Vocabulary", "Familiarity", "Target Overlap", "Size", "Position", "Type", "N Effect Sizes"), caption = "Summary of all papers. Age: mean age (in months). Vocabulary: Comp = comprehension, Prod = production. Distractor Familiarity: Fam = Familiar, Unfam = Unfamiliar  Target Overlap: O = onset, M = medial, C = coda. Mispronunciation Size: number of features changed; commas indicate separate comparison, dashes indicate an aggregated range. Mispronunciation Position: O = onset, M = medial, C = coda. Mispronunciation Type: C = consonant, V = vowel, T = tone. A slash separator indicates no distinction was made in the stimuli and unspec. indicates that the value was unspecified in the paper", landscape = TRUE, font_size = "scriptsize", col_spanners = list(`Distractor` = c(5, 6), `Mispronunciation` = c(7, 9)))

@@

The `r length(unique(descriptive_dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible [@Tsuji2014; @Bergmann2018]. For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results. For the planned analyses to evaluate the development of mispronunciation sensitivity and modulating factors, we focus on the following characteristics: 1) Condition: Were words mispronounced or not; 2) Mean age reported per group of infants, in days; 3) Vocabulary size, measured by a standardized questionnaire or list; 4) Size of mispronunciation, measured in features changed; 5) Position of mispronunciation: onset, medial, coda; 6) Type of mispronunciation: consonant, vowel, or both; 7) Phonological overlap between target and distractor: onset, medial, coda, none; 8) Distractor familiarity: familiar or unfamiliar. A detailed explanation for moderating factors 3-8 can be found in their respective sections in the Results [^1]. We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  [e.g., consonant versus vowel mispronunciations; @Mani2007].  The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were `r nrow(descriptive_dat)` records in our data.

@@

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers). Two papers reported raw means and standard deviations for some records and just t-values for the remaining records [@Swingley2016; @Altvater2014]. Raw means and standard deviations were extracted from figures for `r with(descriptive_dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participant design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance. Upon request we were provided with correlation values for one paper [@Altvater2010]; we were able to compute correlations using means, standard deviations, and t-values for `r with(corr_info, n_unique[imputed_corr == "no"])` papers [following @Csibra2016; see also @Rabagliati2018]. Correlations were imputed for the remaining papers [@Bergmann2016]. For two papers, we could not derive any effect size [@Ballem2005; @Renner2017], and for a third paper, we do not have sufficient information in one record to compute effect sizes [@Skoruppa2013]. We compute a total of `r sum(dat$is_mp == 0)+n_outlier_correct` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)+n_outlier_MP` for mispronunciations. Following standard meta-analytic practice, we remove outliers, i.e. effect sizes more than 3 standard deviations from the respective mean effect size. This leads to the exclusion of `r n_outlier_correct` records for correct pronunciations and `r n_outlier_MP` records for mispronunciations.

@@

Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper. Over half of the records (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score. The Difference Score is one value, which is then compared with a chance value of 0. In contrast, Pre vs. Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records), directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g. t-test, ANOVA). This requires two values, one for the pre-naming phase and one for the post-naming phase. The remaining records used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` records), which compares the post-naming PTL score with a chance value of 50%. Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%). Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

@@

```{r FunnelCombo, echo = FALSE, fig.width=7,fig.height=4, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size. The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot asymmetry.", results="hide"}

@@

@@

sum_eff_misp <- coef(summary(rma_MP))[1,]

@@

We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels. The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)`, a large effect, which was significantly different from zero `r CI_p(sum_eff)` with a CI lower bound of `r r2(sum_eff$ci.lb)`. We then calculated the meta-analytic effect for object identification in response to mispronounced words. In this case, the variance-weighted meta-analytic effect size was `r g_SE(sum_eff_misp)`, a small effect, which was also significantly different from zero `r CI_p(sum_eff_misp)`. When presented with a correct or mispronounced label, infants fixated the correct object.

@@

The above two analyses considered the data from mispronounced and correctly pronounced words separately. To evaluate mispronunciation sensitivity, we compared the effect size Hedges' *g* for correct pronunciations with mispronunciations directly. To this end, we combined the two datasets. When condition was included (correct, mispronounced), the moderator test was significant (`r mod_test(rma_MPeffect)`). The estimate for mispronunciation sensitivity was `r g_SE(sum_eff)`, and infants' looking behavior across conditions was significantly different `r CI_p(sum_eff)`. This confirms that although infants fixate the correct object for both correct pronunciations and mispronunciations, the observed fixations to target (as measured by the effect sizes) were significantly greater for correct pronunciations, suggesting sensitivity to mispronunciations.

@@

The estimated effect for mispronunciation sensitivity in this meta-analysis is `r mp_effect`, and the median sample size is `r median_sample` participants. If we were to assume that researchers assess mispronunciation sensitivity in a simple paired t-test, the resulting power is `r ptt_power`%. In other words, only about half the studies should report a significant result even with a true population effect. Reversely, to achieve 80% power, one would need to test `r round(ptt.est$n, 0)` participants.

@@

### Vocabulary Correlations

@@
